prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2023-01-13 inst/MyArticle/paper.Rmd
caption

```{r tableOverview}
caption = "Rows - R packages, Columns - types of models supported: pd - parallel design, rm - repeated measurements, fd - factorial design, int - interactions among factors, mem - mixed effect models, eb - empirical Bayes, md - missing data modelling with no imputation needed. Y - yes"

>>>>

```{r tableOverview}
caption = "Rows - R packages, Columns - types of models supported: pd - parallel design, rm - repeated measurements, fd - factorial design, int - interactions among factors, mem - mixed effect models, eb - empirical Bayes, md - missing data modelling (no imputation needed). Y - yes"
